Shifting Shadows of the Six: Decoding Toronto's Crime Trends from 2014 to 2023

### 2024-01-23 outputs/paper/paper.qmd
Added references

* **Data Transformation:** Converting the dataset from a wide format to a long format for easier manipulation using the `tidyr` package.

* **Aggregation:** Summarizing the data by year and crime type using the `dplyr` package.

>>>>

* **Data Transformation:** Converting the dataset from a wide format to a long format for easier manipulation using the `tidyr`[@citetidyr] package.

* **Aggregation:** Summarizing the data by year and crime type using the `dplyr`[@citedplyr] package.
